---
title: "S1: behavioural analysis with brms - hypothesis-guided and explorative"
author: "I. S. Plank"
date: "`r Sys.Date()`"
output: pdf_document
---
  
```{r settings, include=FALSE}

knitr::opts_chunk$set(echo = T, warning = F, message = F, fig.align = 'center', fig.width = 9)
ls.packages = c("knitr",# kable
    "ggplot2",          # plots
    "brms",             # Bayesian lmms
    "designr",          # simLMM
    "bridgesampling",   # bridge_sampler
    "tidyverse",        # tibble stuff
    "ggpubr",           # ggarrange
    "ggrain",           # geom_rain
    "bayesplot",        # plots for posterior predictive checks
    "SBC",              # plots for checking computational faithfulness
    "rstatix",          # anova
    "BayesFactor", 
    "bayestestR"        # equivalence_test
)

lapply(ls.packages, library, character.only=TRUE)

# set cores
options(mc.cores = parallel::detectCores())

# set options for SBC
use_cmdstanr = getOption("SBC.vignettes_cmdstanr", TRUE) # Set to false to use rstan instead
options(brms.backend = "cmdstanr")

# using parallel processing
library(future)
plan(multisession)

# Setup caching of results
cache_dir = "./_brms_SBC_cache"
if(!dir.exists(cache_dir)) {
  dir.create(cache_dir)
}

# graph settings 
c_light = "#a9afb2"; c_light_highlight = "#8ea5b2"; c_mid = "#6b98b2" 
c_mid_highlight = "#3585b2"; c_dark = "#0072b2"; c_dark_highlight = "#0058b2" 
c_green = "#009E73"
sz = 1

# custom colour palette
custom.col = c(c_dark_highlight, "#CC79A7", "#009E73", "#D55E00")

```

<style type="text/css">
  .main-container {
    max-width: 1100px;
    margin-left: auto;
    margin-right: auto;
  }
</style>
  
# S1.1 Introduction
  
This R Markdown script analyses data from the MSYNC project. The data was preprocessed before being read into this script. 

## Some general settings

```{r set}

# number of simulations
nsim = 500

# set number of iterations and warmup for models
iter = 3000
warm = 1000

# set the seed
set.seed(2468)

```

## Package versions

The following packages are used in this RMarkdown file: 
  
```{r lib_versions, echo=F}

print(R.Version()$version.string)

for (package in ls.packages) {
  print(sprintf("%s version %s", package, packageVersion(package)))
}

```

## General info

We planned to determine the group-level effect subjects following Barr (2013). For each model, experiment specific priors were set based on previous literature or the task (see comments in the code).

We perform prior predictive checks as proposed in Schad, Betancourt and Vasishth (2020) using the SBC package. To do so, we create `r nsim` simulated datasets where parameters are simulated from the priors. These parameters are used to create one fake dataset. Both the true underlying parameters and the simulated discrimination values are saved. 

Then, we create graphs showing the prior predictive distribution of the simulated discrimination threshold to check whether our priors fit our general expectations about the data. Next, we perform checks of computational faithfulness and model sensitivity as proposed by Schad, Betancourt and Vasishth (2020) and implemented in the SBC package. We create models for each of the simulated datasets. Last, we calculate performance metrics for each of these models, focusing on the population-level parameters. Most simulation-based calibrations were  performed on the original models with three diagnostic groups. Since priors, data points per comparison and model formula did not change, we assume that the SBC holds for the model with four diagnostic groups. 

## Preparation and group comparisons

First, we load the data and combine it with demographic information including the diagnostic status of the subjects. Then, all predictors are set to sum contrasts. 

```{r prep_data}

# check if the data file exists, if yes load it:
if (!file.exists("MSYNC_data.RData")) {
  
  # set the data path
  dt.path  = "/media/emba/emba-2/MSYNC/data"

  # get demo info for subjects
  df.sub = read_csv(file.path(dt.path, "df_centraXX_final.csv"), 
                    show_col_types = F)
  
  # anonymise everything [!ADD]
  
  # load excluded participants (low accuracy)
  #exc = scan(file.path(dt.path, 'FER-exc.txt'), what="character", sep=NULL)
  
  #df.exc = df.sub %>% 
  #  filter(subID %in% exc) %>% 
  #  count()
}

p1 = ggplot(df.sub, aes(x = IRI_final)) + 
  geom_density(fill = c_mid_highlight, alpha = 0.66) +
  labs(title = "Distribution of individual Interpersonal Reactivity", y = "", x = "") +
  theme_bw()

p2 = ggplot(df.sub, aes(x = RAADS_final)) + 
  geom_density(fill = c_mid_highlight, alpha = 0.66) +
  labs(title = "Distribution of individual RADS-R", y = "", x = "") +
  theme_bw()

# [!ADD] distributions of the dyadic similarity measures

ggarrange(p1, p2, ncol = 2)

```
