---
title: "Supplementary materials"
subtitle: "MSYNC - Conversation Task"
author: "I. S. Plank"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    number_sections: true
pdf-engine: lualatex
fontsize: 10pt
geometry: margin=12mm
execute:
  warning: false
header-includes:
# Add the S before section, figure and table numbers
- \renewcommand{\thesection}{S\arabic{section}}
- \renewcommand{\thetable}{S\arabic{table}} 
- \renewcommand{\thefigure}{S\arabic{figure}} 
---

```{r settings, include=FALSE}

knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.align = 'center', 
                      fig.width = 7.5, fig.height = 4)
ls.packages = c("knitr",# kable
    "brms",             # Bayesian lmms
    "tidyverse",        # tibble stuff
    "ggpubr",           # ggarrange
    "bayesplot",        # plots for posterior predictive checks
    "rstatix",          # anova
    "corrplot",         # correlation plots, corrplot
    "BayesFactor", 
    "FactoMineR",       # pca
    "easystats",        # equivalence_test, correlation
    "psych"             # unidim
)

# if packman is not installed yet, install it
if(!("pacman" %in% installed.packages()[,"Package"])) install.packages("pacman")
pacman::p_load(char = ls.packages) 

# set cores
options(mc.cores = parallel::detectCores())

# set option for reading in data
options(readr.show_col_types = FALSE)

# set options for brms
options(brms.backend = "cmdstanr")

# using parallel processing
library(future)
plan(multisession)

# Setup caching of results
brms_dir = "./_brms_models"
if(!dir.exists(brms_dir)) {
  dir.create(brms_dir)
}

# scale function for vector
scale_this = function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

# create string of packages
txt = ''
for (package in ls.packages) {
  txt = sprintf("%s%s version %s; ", txt, package, packageVersion(package))
}

c_light = "#a9afb2"; c_dark = "#0072b2"

```

# Introduction

This R Markdown script analyses Conversation Task data from the MSYNC project. The data was preprocessed before being read into this script. Here, we focus on the behavioural and the eye-tracking data. We use the following abbreviations:

-   IPS : interpersonal synchrony between two interaction partners
-   IPA : interpersonal adaptation, the amount one person adapts their behaviour to their interaction partner's behaviour
-   QSE : quality of the social experience, collected through several self-reported measures

```{r set}

# number of simulations
nsim = 500

# set number of iterations and warmup for models
iter = 3000
warm = 1000

# set the seed
set.seed(2468)

```

## Package versions

We used `r R.Version()$version.string` and the following packages in the creation of this document: `r txt`

## General info

We performed prior predictive checks as proposed in Schad, Betancourt and Vasishth (2020) using the SBC package in a separate file. All categorical predictors are set to sum-coding and all continuous predictors and outcomes are scaled. Names of scaled variables are preceded by an s to indicate the scaling.

## Preparation and group comparisons

First, we load the data and combine it with demographic information including the diagnostic status of the subjects. Then, we print some basic information on the participants and dyads.

```{r prep_data}

# load the CT data:
load("MSYNC_data-CT.RData")

# gender distribution
tb.gen = xtabs(~ gender + cis, data = df.indi |> 
                 mutate(cis = if_else(gender_identity == "Ja", "cisgender", "transgender")))

# handedness
tb.hnd = xtabs(~ handedness, data = df.indi)

kable(
  list(tb.gen, tb.hnd,  
       df.dyad |> group_by(order, dyad.gender) |> count()),
  caption = 'Participant and dyad counts for different demo variables.')

df.sum = df.indi |> select(c("age", "edu", "RAADS_final", "IRI_final", "ADC_final", 
                             "CFT_iq", "ECR")) |>
  pivot_longer(cols = everything(), names_to = "measurement") |>
  group_by(measurement) |>
  summarise(
    overall = sprintf("%.2f ±%.2f (%.0f to %.0f)", 
                      mean(value, na.rm = T), 
                      sd(value, na.rm = T), 
                      min(value, na.rm = T), 
                      max(value, na.rm = T))
  )
  

kable(merge(df.demo, df.sum) |> arrange(bf.log) |>
        mutate(bf.log = 
                 if_else(
                   bf.log > log(3), 
                   sprintf("%.3f*", bf.log),
                   sprintf("%.3f", bf.log))),
      caption = "Demographic information and questionnaire values")


```

The interaction partner in one dyad differed `r sprintf("%.2f ±%.2f (%.0f to %.0f)", mean(df.dyad$dyad.age), sd(df.dyad$dyad.age), min(df.dyad$dyad.age), max(df.dyad$dyad.age))` years from each other.

## Assessing the relationship between motion quantity and motion IPSmov

```{r mov}

# compute correlations on the dyad level
kable(df.dyad.ct.mea |> 
  group_by(order) |>
  correlation(bayesian = T, select = 'MEA.total.mov',
              select2 = c('MEA.mean', 'MEA.peak', 'MEA.plag', 'MEA.zero')) |>
  select(Group, Parameter2, rho, CI_low, CI_high, pd) |>
  # only print the credible ones
  filter(pd > 0.975) |>
  # highlight the credible ones
  mutate(credible = if_else(pd > 0.975, '*', '')), 
  digits = 4, caption = "Credible correlations on dyad level for CT")

# compute correlations on the individual level > first for CT
kable(df.indi.ct.mea |> 
  group_by(order) |>
  correlation(bayesian = T, select = 'MEA.total.mov',
              select2 = c('MEA.mean', 'MEA.peak', 'MEA.plag')) |>
  select(Group, Parameter2, rho, CI_low, CI_high, pd) |>
  # only print the credible ones
  filter(pd > 0.975) |>
  # highlight the credible ones
  mutate(credible = if_else(pd > 0.975, '*', '')), 
  digits = 4, caption = "Credible correlations on individual level for CT")

```

Since movement quantity and peak as well as average IPSmov/IPAmov are highly correlated in the conversation task, we will add this into our model as a predictor of no interest.

## Assessing the uniformity of QSE

We want to aggregate several scores from our questionnaires to measure the quality of the QSE. Thus, we check now if these scores are likely to measure one uniform concept. 

```{r uni}

print("CT")
rel.ct = unidim(df.indi |> 
  select(ends_with(".sCT")))
rel.ct

M = cor(df.indi |> select(ends_with(".sCT")))
testRes = cor.mtest(df.indi |> select(ends_with(".sCT")), conf.level = 0.95)
corrplot.mixed(M, order = 'AOE', tl.pos = "lt", p.mat = testRes$p, 
               insig = "blank", number.cex = 0.75, tl.cex = 0.5)

```

## Setting weakly informed priors

We will use the same priors for all of our models except the Bernoulli model which got its own priors.

```{r priors}

priors = c(
  prior(normal(0,    0.10),  class = Intercept), # because standardised
  prior(normal(1.0,  0.50),  class = sigma),
  prior(normal(0.5,  0.50),  class = sd),        # less than sigma
  prior(normal(0,    0.30),  class = b)          # small to medium effect
)

kable(priors, caption = "Priors for all Gaussian linear (mixed) models")  

# Bernoulli
priors.b = c(
  prior(normal(0,    0.50),  class = Intercept), # because allocated 50:50
  prior(normal(0,    1.00),  class = b)
)

kable(priors.b, caption = "Priors for the Bernoulli linear model")  

```

# Testing effect of order on IPSmov

## Model setup

```{r model_ct}

# set the contrast
contrasts(df.dyad.ct.mea$order) = contr.sum(2)
contrasts(df.dyad.ct.mea$order)

# code for filenames
code = "CT_order"

# scale the variables
df.dyad.ct.mea = df.dyad.ct.mea |>
     mutate(across(where(is.numeric), 
                   .fns = scale_this,
                   .names = "s{col}" ) )

# model formula
f = brms::bf( sMEA.mean ~ order + sMEA.total.mov)
f

```

## Posterior predictive checks

As the next step, we fit the model, check whether there are divergence or rhat issues, and then check whether the chains have converged.

```{r postpc_ct1, fig.height=2, message=T}

# fit the final model
m = brm(f,
        df.dyad.ct.mea, 
        prior = priors |> filter(class != "sd"),
        iter = iter, warmup = warm,
        backend = "cmdstanr", threads = threading(8),
        file = file.path(brms_dir, sprintf("m_%s", code)),
        save_pars = save_pars(all = TRUE),
        seed = 2684
        )
rstan::check_hmc_diagnostics(m$fit)

# check that rhats are below 1.01
sum(brms::rhat(m) >= 1.01, na.rm = T)

# check the trace plots
post.draws = as_draws_df(m)
mcmc_trace(post.draws, regex_pars = "^b_",
           facet_args = list(ncol = 3)) +
  scale_x_continuous(breaks=scales::pretty_breaks(n = 3)) +
  scale_y_continuous(breaks=scales::pretty_breaks(n = 3))

```

This model has no pathological behaviour with E-BFMI, no divergent sample and no rhats that are higher or equal to 1.01. Therefore, we go ahead and perform our posterior predictive checks.

```{r postpc_ct2, fig.height=2}

# get posterior predictions
post.pred = posterior_predict(m, ndraws = nsim)

# check the fit of the predicted data compared to the real data
p1 = pp_check(m, ndraws = nsim) + 
  theme_bw() + theme(legend.position = "none")

# distributions of means compared to the real values per group
p2 = ppc_stat_grouped(df.dyad.ct.mea$sMEA.mean, post.pred, df.dyad.ct.mea$order) + 
  theme_bw() + theme(legend.position = "none")

p = ggarrange(p1, p2, 
          nrow = 1, ncol = 2, labels = "AUTO")
annotate_figure(p, top = text_grob("Posterior predictive checks", 
                                   face = "bold", size = 14))

```

The overall simulated data (in lightblue) fits the real data (in dark blue) reasonably well, even though it does not reproduce the shape completely. The mean simulated data based on the model fits well with the real data.

## Inferences

Now that we are convinced that we can trust our model, we have a look at its estimates.

```{r inf_ct, fig.height=2, fig.width=4}

# print a summary
summary(m)

# plot the posterior distributions
post.draws |> 
  select(starts_with("b_")) |>
  pivot_longer(cols = starts_with("b_"), names_to = "coef", values_to = "estimate") |>
  subset(!startsWith(coef, "b_Int")) |>
  mutate(
    coef = substr(coef, 3, nchar(coef)),
    coef = str_replace_all(coef, "order1", "CT-MG"),
    coef = fct_reorder(coef, desc(estimate))
  )  |> 
  group_by(coef) |>
  mutate(
    cred = case_when(
      (mean(estimate) < 0 & quantile(estimate, probs = 0.95) < 0) |
        (mean(estimate) > 0 & quantile(estimate, probs = 0.05) > 0) ~ "credible",
      T ~ "not credible"
    )
  ) |> ungroup() |>
  ggplot(aes(x = estimate, y = coef, fill = cred)) +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  ggdist::stat_halfeye(alpha = 0.7) + ylab(NULL) +
  scale_fill_manual(values = c("credible" = c_dark, "not credible" = c_light)) + 
  theme_bw() + theme(legend.position = "bottom", legend.direction = "horizontal")

# "CT-MG" < "MG-CT"
h.ct = hypothesis(m, "0 > 2*order1")

```

Assessing the effect of order on mean IPS results in the following *estimate* = `r round(h.ct$hypothesis$Estimate,2)` [`r round(h.ct$hypothesis$CI.Lower,2)`, `r round(h.ct$hypothesis$CI.Upper,2)`] (*posterior probability* = `r round(h.ct$hypothesis$Post.Prob*100,2)`%); thus, this suggests a `r interpret_cohens_d(h.ct$hypothesis$Estimate)` effect of order on IPS of movement in the Conversation Task. 

## Rerun focusing on dyads passing the pseudo-IPSmov test

Our comparison between pseudo-IPSmov and IPSmov did not reveal higher IPSmov across the board, but only for two-thirds of the sample. Therefore, we rerun the model on those dyads to ensure that the conclusions hold.

```{r postpc_ct_sel1, fig.height=2, message=T}

# select only the dyads for which pseudo-IPSmov based on segments lower than IPSmov
df.sel = df.dyad.ct.mea |>
  filter(dyad %in% df.dyad[df.dyad$relevant == "credible",]$dyad)

# fit the final model
m = brm(f,
        df.sel, prior = priors |> filter(class != "sd"),
        iter = iter, warmup = warm,
        backend = "cmdstanr", threads = threading(8),
        file = file.path(brms_dir, sprintf("m_%s_sel", code)),
        save_pars = save_pars(all = TRUE),
        seed = 2684
        )
rstan::check_hmc_diagnostics(m$fit)

# check that rhats are below 1.01
sum(brms::rhat(m) >= 1.01, na.rm = T)

# check the trace plots
post.draws = as_draws_df(m)
mcmc_trace(post.draws, regex_pars = "^b_",
           facet_args = list(ncol = 3)) +
  scale_x_continuous(breaks=scales::pretty_breaks(n = 3)) +
  scale_y_continuous(breaks=scales::pretty_breaks(n = 3))

```

```{r postpc_ct_sel2, fig.height=2}

# get posterior predictions
post.pred = posterior_predict(m, ndraws = nsim)

# check the fit of the predicted data compared to the real data
p1 = pp_check(m, ndraws = nsim) + 
  theme_bw() + theme(legend.position = "none")

# distributions of means compared to the real values per group
p2 = ppc_stat_grouped(as.numeric(df.sel$sMEA.mean), post.pred, df.sel$order) + 
  theme_bw() + theme(legend.position = "none")

p = ggarrange(p1, p2, 
          nrow = 1, ncol = 2, labels = "AUTO")
annotate_figure(p, top = text_grob("Posterior predictive checks", 
                                   face = "bold", size = 14))

```

```{r inf_ct_sel, fig.height=2, fig.width=4}

# print a summary
summary(m)

# plot the posterior distributions
post.draws |> 
  select(starts_with("b_")) |>
  pivot_longer(cols = starts_with("b_"), names_to = "coef", values_to = "estimate") |>
  subset(!startsWith(coef, "b_Int")) |>
  mutate(
    coef = substr(coef, 3, nchar(coef)),
    coef = str_replace_all(coef, "order1", "CT-MG"),
    coef = fct_reorder(coef, desc(estimate))
  )  |> 
  group_by(coef) |>
  mutate(
    cred = case_when(
      (mean(estimate) < 0 & quantile(estimate, probs = 0.95) < 0) |
        (mean(estimate) > 0 & quantile(estimate, probs = 0.05) > 0) ~ "credible",
      T ~ "not credible"
    )
  ) |> ungroup() |>
  ggplot(aes(x = estimate, y = coef, fill = cred)) +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  ggdist::stat_halfeye(alpha = 0.7) + ylab(NULL) +
  scale_fill_manual(values = c("credible" = c_dark, "not credible" = c_light)) + 
  theme_bw() +  theme(legend.position = "bottom", legend.direction = "horizontal")

# "CT-MG" < "MG-CT"
h.ct2 = hypothesis(m, "0 > 2*order1")

```

Assessing the effect of order on mean IPS for these dyads only results in the following *estimate* = `r round(h.ct2$hypothesis$Estimate,2)` [`r round(h.ct2$hypothesis$CI.Lower,2)`, `r round(h.ct2$hypothesis$CI.Upper,2)`] (*posterior probability* = `r round(h.ct2$hypothesis$Post.Prob*100,2)`%); thus, this suggests a `r interpret_cohens_d(h.ct2$hypothesis$Estimate)` effect of order on IPS of movement in the Conversation Task when only considering dyads for which pseudo-IPS exceeded observed IPS. 

# Exploring increasing social experience across the experiment

```{r model_ct_qset}

code = "CT_qse-task"

df.qse = df.indi |>
  select(subID, dyad, order, soc.exp.CT, soc.exp.MG) |>
  mutate(
    QSE.first  = if_else(order == "MG-CT", soc.exp.MG, soc.exp.CT),
    QSE.second = if_else(order != "MG-CT", soc.exp.MG, soc.exp.CT)
  ) |>
  mutate(across(c(QSE.first, QSE.second), scale_this, .names = "s{.col}")) |>
  mutate(order = as.factor(order))
  

contrasts(df.qse$order) = contr.sum(2)
contrasts(df.qse$order)

# model formula
f = brms::bf( sQSE.second ~ sQSE.first * order + (1 | dyad) )
f


```

```{r postpc_ct_qset1, fig.height=2, message=T}

# fit the final model
m = brm(f,
        df.qse, prior = priors,
        iter = iter, warmup = warm,
        backend = "cmdstanr", threads = threading(8),
        file = file.path(brms_dir, sprintf("m_%s", code)),
        save_pars = save_pars(all = TRUE),
        seed = 8484
        )
rstan::check_hmc_diagnostics(m$fit)

# check that rhats are below 1.01
sum(brms::rhat(m) >= 1.01, na.rm = T)

# check the trace plots
post.draws = as_draws_df(m)
mcmc_trace(post.draws, regex_pars = "^b_",
           facet_args = list(ncol = 4)) +
  scale_x_continuous(breaks=scales::pretty_breaks(n = 3)) +
  scale_y_continuous(breaks=scales::pretty_breaks(n = 3))

```

This model has no pathological behaviour with E-BFMI, no divergent sample and no rhats that are higher or equal to 1.01. Therefore, we go ahead and perform our posterior predictive checks.

```{r postpc_ct_qset2, fig.height=2}

# check the fit of the predicted data compared to the real data
p = pp_check(m, ndraws = nsim) + 
  theme_bw() + theme(legend.position = "none")

annotate_figure(p, top = text_grob("Posterior predictive checks", 
                                   face = "bold", size = 14))

```

The overall simulated data fits reasonably well. Now that we are convinced that we can trust our model, we have a look at its estimates.

```{r inf_ct_qset1, fig.height=3.25, fig.width=4}

# print a summary
summary(m)

# plot the posterior distributions
post.draws |> 
  select(starts_with("b_")) |>
  pivot_longer(cols = starts_with("b_"), names_to = "coef", values_to = "estimate") |>
  subset(!startsWith(coef, "b_Int")) |>
  mutate(
    coef = substr(coef, 3, nchar(coef)),
    coef = fct_reorder(coef, desc(estimate))
  )  |> 
  group_by(coef) |>
  mutate(
    cred = case_when(
      (mean(estimate) < 0 & quantile(estimate, probs = 0.975) < 0) |
        (mean(estimate) > 0 & quantile(estimate, probs = 0.025) > 0) ~ "credible",
      T ~ "not credible"
    )
  ) |> ungroup() |>
  ggplot(aes(x = estimate, y = coef, fill = cred)) +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  ggdist::stat_halfeye(alpha = 0.7) + ylab(NULL) +
  scale_fill_manual(values = c("credible" = c_dark, "not credible" = c_light)) + 
  theme_bw() +  theme(legend.position = "bottom", legend.direction = "horizontal")

e.qse = hypothesis(
  m, 
  c(
    "order1*2 > 0",
    "sQSE.first > 0",
    "sQSE.first + sQSE.first:order1 > 0", # order CT-MG slope
    "sQSE.first - sQSE.first:order1 > 0", # order MG-CT slope
    "2 * sQSE.first:order1 > 0"           # slope difference
  ), alpha = 0.025)

kable(e.qse$hypothesis |>
        cbind(data.frame(
          Effect = c("Order effect", "Overall slope", "CT-MG slope", "MG-CT slope", "Slope difference")
        )) |> relocate(Effect), digits = 3, caption = "Development of social experience across task")

```

```{r inf_ct_qset2, fig.height=4}

df.qse |> 
  mutate(order = if_else(order == "MG-CT", 
                         "Mirror Game first",
                         "Movement first")) |> 
  mutate_if(is.character, as.factor) |>
  ggplot(aes(x = QSE.first, y = QSE.second, fill = order, colour = order)) + #
  geom_point(size = 2, alpha = 0.5) +     
  geom_smooth(method = "lm", alpha = 0.25) +
  theme_bw() + ylim(0.25, 1) + xlim(0.25, 1) + 
  theme(legend.position = "bottom", 
        plot.title = element_text(hjust = 0.5), 
        legend.direction = "horizontal", legend.title = element_blank(),
        text = element_text(size = 15),
        axis.text.x = element_text(size = 14),
        axis.title.y = element_text(size = 14))

```

# Exploring mediation analysis

## Model setup

```{r model_ct_qse}

# code for filenames
code = "CT_mediation"

# scale the variables
df.ct.mea.qse = 
  merge(df.dyad.ct.mea |>
          select(order, dyad, MEA.mean, MEA.total.mov), 
        df.indi |> select(order, subID, dyad, soc.exp.CT) |>
          group_by(order, dyad) |>
          summarise(
            soc.exp.CT = mean(soc.exp.CT),
            .groups = "drop"
          )) |>
  mutate(across(where(is.numeric), 
               .fns = scale_this,
               .names = "s{col}" ) ) |>
  mutate_if(is.character, as.factor)

# set the contrast
contrasts(df.ct.mea.qse$order) = contr.sum(2)
contrasts(df.ct.mea.qse$order)

# model formula
f.QSE = brms::bf( ssoc.exp.CT ~ order + sMEA.mean + sMEA.total.mov)
f.IPS = brms::bf( sMEA.mean ~ order + sMEA.total.mov)
f.IPS
f.QSE

priors.new = get_prior(f.IPS + f.QSE + set_rescor(FALSE), data = df.ct.mea.qse) |>
  mutate(
    prior = case_when(
      class == "Intercept" ~ "normal(0,   0.1)",
      class == "sigma"     ~ "normal(1,   0.5)",
      class == "sd"        ~ "normal(0.5, 0.5)",
      class == "b"         ~ "normal(0,   0.3)"
    )
  )

```

## Posterior predictive checks

As the next step, we fit the model, check whether there are divergence or rhat issues, and then check whether the chains have converged.

```{r postpc_ct_qse1, fig.height=4, message=T}

# fit the final model
m = brm(f.IPS + f.QSE + set_rescor(FALSE),
        data = df.ct.mea.qse, 
        prior = priors.new,
        iter = iter, warmup = warm,
        backend = "cmdstanr", threads = threading(8),
        file = file.path(brms_dir, sprintf("m_%s", code)),
        save_pars = save_pars(all = TRUE),
        seed = 2684
        )
rstan::check_hmc_diagnostics(m$fit)

# check that rhats are below 1.01
sum(brms::rhat(m) >= 1.01, na.rm = T)

# check the trace plots
post.draws = as_draws_df(m)
mcmc_trace(post.draws, regex_pars = "^b_",
           facet_args = list(ncol = 3)) +
  scale_x_continuous(breaks=scales::pretty_breaks(n = 3)) +
  scale_y_continuous(breaks=scales::pretty_breaks(n = 3))

```

This model has no pathological behaviour with E-BFMI, no divergent sample and no rhats that are higher or equal to 1.01. Therefore, we go ahead and perform our posterior predictive checks.

```{r postpc_ct_qse2, fig.height=2}

# check the fit of the predicted data compared to the real data
p1 = pp_check(m, ndraws = nsim, resp = "ssocexpCT") + 
  theme_bw() + theme(legend.position = "none") + labs(title = "QSE")

p2 = pp_check(m, ndraws = nsim, resp = "sMEAmean") + 
  theme_bw() + theme(legend.position = "none") + labs(title = "IPS")

p = ggarrange(p1, p2, 
          nrow = 1, ncol = 2, labels = "AUTO")
annotate_figure(p, top = text_grob("Posterior predictive checks", 
                                   face = "bold", size = 14))

```

The overall simulated data (in lightblue) fits the real data (in dark blue) reasonably well, even though it does not reproduce the shape completely. The mean simulated data based on the model fits well with the real data.

## Inferences

Now that we are convinced that we can trust our model, we have a look at its estimates.

```{r inf_ct_qse, fig.height=3, fig.width=4}

# print a summary
summary(m)

# summary statistics for mediation analysis
df.med = post.draws |>
  mutate(
    "Order -> IPS -> QSE.CT" = b_sMEAmean_order1 * -2 * b_ssocexpCT_sMEA.mean,
    "Order -> IPS" = b_sMEAmean_order1 * -2, 
    "Order -> QSE.CT" = b_ssocexpCT_order1 * -2, 
    "Total Effect" =  b_sMEAmean_order1 * -2 * b_ssocexpCT_sMEA.mean + b_ssocexpCT_order1 * -2
  ) |>
  rename("IPS -> QSE.CT" = b_ssocexpCT_sMEA.mean) |>
  select(contains("->"), "Total Effect")
  
df.med.agg = df.med |>
  pivot_longer(cols = everything(), names_to = "Parameter") |>
  group_by(Parameter) |>
  summarise(
    Estimate = sprintf("%.3f +- %.3f [%.3f, %.3f]",
                       mean(value), sd(value), 
                       quantile(value, 0.025, names = F),
                       quantile(value, 0.975, names = F)),
    `Posterior Probability` = if_else(mean(value) > 0, 
                                      mean(value > 0)*100,
                                      mean(value < 0)*100)
  )

equ = equivalence_test(df.med, range = c(-0.1, 0.1))

kable(merge(df.med.agg, equ) |>
    mutate(ROPE = ROPE_Percentage * 100, 
           `ROPE Interpretation` = ROPE_Equivalence, 
           HDI = sprintf("[%.2f, %.2f]", HDI_low, HDI_high)) |> 
      select(-CI, -contains("_")), digits = 2,
      caption = "Results of the explorative mediation analysis")

```

# Exploring individual experience and behaviour in CT: extracting principal components

```{r ct_pca}

# check if PCA file exists
if (!file.exists(file.path(brms_dir, "df_pca_CT.rds"))) {
  # create a new dataframe with all the info
  df.indi.ct.pc = df.indi |> 
    select(subID, dyad, order, soc.exp.CT) |>
    # add the information from MEA
    merge(df.indi.ct.mea) |>
    # add the information from openface
    merge(df.indi.ct.of |> 
            pivot_wider(names_from = key, 
                        values_from = c(OF.mean, OF.peak, OF.plag))) |>
    # add the face dwell time from the eye tracking
    merge(df.indi.ct.et |> select(subID, dwell.face, FI, SI, SI.ratio, SI.FI)) |>
    mutate_if(is.character, as.factor) |> drop_na()
  # extract the features to be used
  df.indi.ct.pc.features = df.indi.ct.pc |> 
    select(where(is.numeric), -soc.exp.CT)
  # normalise them
  data.norm = scale(df.indi.ct.pc.features)
  # perform the PCA
  pca = princomp(data.norm)
  saveRDS(pca, file.path(brms_dir, "pca_CT.rds"))
  # add components to the data frame to explain 2/3 of the variance
  df.indi.ct.pc$pc1 = pca$scores[,1]
  df.indi.ct.pc$pc2 = pca$scores[,2]
  df.indi.ct.pc$pc3 = pca$scores[,3]
  df.indi.ct.pc$pc4 = pca$scores[,4]
  saveRDS(df.indi.ct.pc, file.path(brms_dir, "df_pca_CT.rds"))
} else {
  pca = readRDS(file.path(brms_dir, "pca_CT.rds"))
  df.indi.ct.pc = readRDS(file.path(brms_dir, "df_pca_CT.rds"))
}

fa.parallel(df.indi.ct.pc |> 
              select(where(is.numeric), -soc.exp.CT, -starts_with("pc")), 
            fa = "pc", plot = T)

var_explained = pca$sdev^2 / sum(pca$sdev^2)
cum_var = cumsum(var_explained)

```

In total, there are `r ncol(pca$scores)` components, of which `r which(cum_var > 2/3)[1]` are needed to explain at least 2/3 and `r which(cum_var > 0.9)[1]` to explain more than 90% of the variance. 

## Predicting order from PCs

We try to predict order by the principal components. Since this is a model with a binary outcome we use a Bernoulli distribution with logit. We code the order `CT-MG` as 0 and the order `MG-CT` as 1. Thus, we need to use different priors here, because we are using a logit link function.

```{r model_ct_pc}

# recode the order and scale the predictors + soc.exp
df.indi.ct.pc = df.indi.ct.pc |>
  mutate(
    order.bin = if_else(order == "MG-CT", 1, 0)
  ) |> mutate(across(c(pc1, pc2, pc3, pc4, soc.exp.CT), scale_this, .names = "s{.col}"))

code = "CT_pcs-bern"

# model formula
f = brms::bf( order.bin ~ spc1 + spc2 + spc3 + spc4 )
f


```

```{r postpc_ct_pc1, fig.height=4, message=T}

# fit the final model
m = brm(f,
        df.indi.ct.pc, prior = priors.b,
        family = bernoulli(link = "logit"),
        iter = iter, warmup = warm,
        backend = "cmdstanr", threads = threading(8),
        file = file.path(brms_dir, sprintf("m_%s", code)),
        save_pars = save_pars(all = TRUE),
        seed = 4284
        )
rstan::check_hmc_diagnostics(m$fit)

# check that rhats are below 1.01
sum(brms::rhat(m) >= 1.01, na.rm = T)

# check the trace plots
post.draws = as_draws_df(m)
mcmc_trace(post.draws, regex_pars = "^b_",
           facet_args = list(ncol = 3)) +
  scale_x_continuous(breaks=scales::pretty_breaks(n = 3)) +
  scale_y_continuous(breaks=scales::pretty_breaks(n = 3))

```

This model has no pathological behaviour with E-BFMI, no divergent sample and no rhats that are higher or equal to 1.01. Therefore, we go ahead and perform our posterior predictive checks.

```{r postpc_ct_pc12, fig.height=2}

# get posterior predictions
post.pred = posterior_predict(m, ndraws = nsim)

# check the fit of the predicted data compared to the real data
p = ppc_bars(df.indi.ct.pc$order.bin, post.pred) + 
  theme_bw() + theme(legend.position = "none")

annotate_figure(p, top = text_grob("Posterior predictive checks", 
                                   face = "bold", size = 14))

```

The overall simulated data fits reasonably well. Now that we are convinced that we can trust our model, we have a look at its estimates.

```{r inf_ct_pc1, fig.height=4.25, fig.width=4}

# print a summary
summary(m)

# plot the posterior distributions
df.m = post.draws |> 
  select(starts_with("b_"))

# plot the posterior distributions
df.m |>
  select(starts_with("b_")) |>
  pivot_longer(cols = starts_with("b_"), names_to = "coef", values_to = "estimate") |>
  subset(!startsWith(coef, "b_Int")) |>
  mutate(
    coef = substr(coef, 3, nchar(coef)),
    coef = str_replace_all(coef, "order1", "CT-MG"),
    coef = fct_reorder(coef, desc(estimate))
  )  |> 
  group_by(coef) |>
  mutate(
    cred = case_when(
      (mean(estimate) < 0 & quantile(estimate, probs = 0.975) < 0) |
        (mean(estimate) > 0 & quantile(estimate, probs = 0.025) > 0) ~ "credible",
      T ~ "not credible"
    )
  ) |> ungroup() |>
  ggplot(aes(x = estimate, y = coef, fill = cred)) +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  ggdist::stat_halfeye(alpha = 0.7) + ylab(NULL) +
  scale_fill_manual(values = c("credible" = c_dark, "not credible" = c_light)) + 
  theme_bw() +  theme(legend.position = "bottom", legend.direction = "horizontal")

# create a table with the hypothesis tests for each of the PCs
df.hyp = data.frame()
for (i in 1:4) {
  e = hypothesis(m, sprintf("0 < spc%d", i), alpha = 0.025 )
  if (e$hypothesis$Post.Prob < 0.5) e = hypothesis(m, sprintf("0 > spc%d", i), alpha = 0.025 )
  df.hyp = rbind(df.hyp, 
                 data.frame(
                   Parameter = sprintf("spc%d", i),
                   Est = e$hypothesis$Estimate,
                   Estimate  = sprintf("%.3f ± %.3f [%.3f, %.3f]", 
                                       e$hypothesis$Estimate, e$hypothesis$Est.Error,
                                       e$hypothesis$CI.Lower, e$hypothesis$CI.Upper),
                   Post.Prob = e$hypothesis$Post.Prob
                 ))
}

df.hyp = df.hyp |>
  mutate(
    `Posterior Probability` = if_else(Post.Prob > 0.975, 
                                      sprintf("%.2f*", Post.Prob*100),
                                      sprintf("%.2f", Post.Prob*100)),
    `Effect size` = interpret_cohens_d(Est)
  ) |> select(-Post.Prob, -Est)

# equivalence tests
df.equ = as.data.frame(equivalence_test(m, range = rope_range(m), parameters = "b_spc.*")) |>
  rename(`ROPE Interpretation` = ROPE_Equivalence) |>
  mutate(
    Parameter = sub("b_", "", Parameter),
    ROPE = round(ROPE_Percentage*100,2),
    HDI = sprintf("[%.3f, %.3f]", HDI_low, HDI_high)
  ) |> select(Parameter, ROPE, `ROPE Interpretation`, HDI)
  

# print the outcome of the tests
kable(merge(df.hyp, df.equ), 
      caption = sprintf("Explorative assessment of Bernoulli model predictors (ROPE Range = ±%.3f)",
                        rope_range(m)[2])
)

```


## Predicting social experience from PCs

```{r model_ct_pc_qse}

code = "CT_pcs-exp"

contrasts(df.indi.ct.pc$order) = contr.sum(2)
contrasts(df.indi.ct.pc$order)

# model formula
f = brms::bf( ssoc.exp.CT ~ spc1 + spc2 + spc3 + spc4 + order + (1 | dyad) )
f


```

```{r postpc_ct_pc_qse1, fig.height=4, message=T}

# fit the final model
m = brm(f,
        df.indi.ct.pc, prior = priors,
        iter = iter, warmup = warm,
        backend = "cmdstanr", threads = threading(8),
        file = file.path(brms_dir, sprintf("m_%s", code)),
        save_pars = save_pars(all = TRUE),
        seed = 4284
        )
rstan::check_hmc_diagnostics(m$fit)

# check that rhats are below 1.01
sum(brms::rhat(m) >= 1.01, na.rm = T)

# check the trace plots
post.draws = as_draws_df(m)
mcmc_trace(post.draws, regex_pars = "^b_",
           facet_args = list(ncol = 3)) +
  scale_x_continuous(breaks=scales::pretty_breaks(n = 3)) +
  scale_y_continuous(breaks=scales::pretty_breaks(n = 3))

```

This model has no pathological behaviour with E-BFMI, no divergent sample and no rhats that are higher or equal to 1.01. Therefore, we go ahead and perform our posterior predictive checks.

```{r postpc_ct_pc1_qse2, fig.height=2}

# check the fit of the predicted data compared to the real data
p = pp_check(m, ndraws = nsim) + 
  theme_bw() + theme(legend.position = "none")

annotate_figure(p, top = text_grob("Posterior predictive checks", 
                                   face = "bold", size = 14))

```

The overall simulated data fits reasonably well. Now that we are convinced that we can trust our model, we have a look at its estimates.

```{r inf_ct_pc1_qse, fig.height=4.25, fig.width=4}

# print a summary
summary(m)

# plot the posterior distributions
df.m = post.draws |> 
  select(starts_with("b_"))

# plot the posterior distributions
df.m |>
  select(starts_with("b_")) |>
  pivot_longer(cols = starts_with("b_"), names_to = "coef", values_to = "estimate") |>
  subset(!startsWith(coef, "b_Int")) |>
  mutate(
    coef = substr(coef, 3, nchar(coef)),
    coef = str_replace_all(coef, "order1", "CT-MG"),
    coef = fct_reorder(coef, desc(estimate))
  )  |> 
  group_by(coef) |>
  mutate(
    cred = case_when(
      (mean(estimate) < 0 & quantile(estimate, probs = 0.975) < 0) |
        (mean(estimate) > 0 & quantile(estimate, probs = 0.025) > 0) ~ "credible",
      T ~ "not credible"
    )
  ) |> ungroup() |>
  ggplot(aes(x = estimate, y = coef, fill = cred)) +
  geom_vline(xintercept = 0, linetype = 'dashed') +
  ggdist::stat_halfeye(alpha = 0.7) + ylab(NULL) +
  scale_fill_manual(values = c("credible" = c_dark, "not credible" = c_light)) + 
  theme_bw() +  theme(legend.position = "bottom", legend.direction = "horizontal")

# create a table with the hypothesis tests for each of the PCs
df.hyp = data.frame()
for (i in 1:4) {
  e = hypothesis(m, sprintf("0 > -spc%d", i), alpha = 0.025 )
  if (e$hypothesis$Post.Prob < 0.5) e = hypothesis(m, sprintf("0 < -spc%d", i), alpha = 0.025 )
  df.hyp = rbind(df.hyp, 
                 data.frame(
                   Parameter = sprintf("spc%d", i),
                   Est = e$hypothesis$Estimate,
                   Estimate  = sprintf("%.3f ± %.3f [%.3f, %.3f]", 
                                       e$hypothesis$Estimate, e$hypothesis$Est.Error,
                                       e$hypothesis$CI.Lower, e$hypothesis$CI.Upper),
                   Post.Prob = e$hypothesis$Post.Prob
                 ))
}

df.hyp = df.hyp |>
  mutate(
    `Posterior Probability` = if_else(Post.Prob > 0.975, 
                                      sprintf("%.2f*", Post.Prob*100),
                                      sprintf("%.2f", Post.Prob*100)),
    `Effect size` = interpret_cohens_d(Est)
  ) |> select(-Post.Prob, -Est)

# equivalence tests
df.equ = as.data.frame(equivalence_test(m, range = rope_range(m), parameters = "b_spc.*")) |>
  rename(`ROPE Interpretation` = ROPE_Equivalence) |>
  mutate(
    Parameter = sub("b_", "", Parameter),
    ROPE = round(ROPE_Percentage*100,2),
    HDI = sprintf("[%.3f, %.3f]", HDI_low, HDI_high)
  ) |> select(Parameter, ROPE, `ROPE Interpretation`, HDI)
  

# print the outcome of the tests
kable(merge(df.hyp, df.equ), 
      caption = sprintf("Explorative assessment of Bernoulli model predictors (ROPE Range = ±%.3f)",
                        rope_range(m)[2])
)

```

## PC loadings

```{r pca_load_ct}

df.tbl.pca = as.data.frame(round(pca$loadings[,1:8], 2)) |>
  rename_with(~ sub("Comp\\.", "PC", .x))

# all to get to 90% cumulative variance
kable(df.tbl.pca, caption = "All PCs together explaining >90%")

# focus on the "relevant" ones
kable(df.tbl.pca |> select(PC1, PC2, PC3, PC4) |>
        mutate_if(is.numeric, ~ if_else(abs(.) > 0.10, sprintf("%.2f", .), "")),
      caption = "Most relevant PCs")

```
