---
title: "MSYNC: pseudosynchrony"
author: "I. S. Plank"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    number_sections: true
fontsize: 10pt
geometry: margin=0.5in
---
  
```{r settings, include=FALSE}

knitr::opts_chunk$set(echo = T, warning = F, message = F, fig.align = 'center', fig.width = 8, fig.height = 3)
ls.packages = c("knitr",# kable
    "tidyverse",        # tibble stuff, ggplot
    "ggpubr",           # ggarrange
    "BayesFactor",      # anovaBF
    "effectsize",       # interpretBF
    "ggrain",           # geom_rain
    "rMEA"
)

lapply(ls.packages, library, character.only=TRUE)

# graph settings 
c_light = "#a9afb2"; c_light_highlight = "#8ea5b2"; c_mid = "#6b98b2" 
c_mid_highlight = "#3585b2"; c_dark = "#0072b2"; c_dark_highlight = "#0058b2" 
c_green = "#009E73"
sz = 1
a = 0.5

# custom colour palette
custom.col = c(c_dark_highlight, "#CC79A7", "#009E73", "#D55E00")

# scale function for vector
scale_this = function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

# load pseudosync function
source("pseudosync_fun.R")

# Initialize function to create a fake MEA object out of two vectors
# Input: 
#     * s1, s2: numeric vectors containing the values to be correlated
#     * sampRate: sampling rate per second
#     * s1Name, s2Name: name for the values to be correlated, default is "s1Name" and "s2Name"
# Output:
#     * fake MEA object that pretends to be a MEA object
#
fakeMEA = function(s1, s2, sampRate, s1Name = "s1Name", s2Name = "s2Name") {
  mea = structure(list(all_01_01 = structure(list(MEA = structure(list(
    s1Name = s1, s2Name = s2), row.names = c(NA, -length(s1)), class = "data.frame"), 
    ccf = NULL, ccfRes = NULL), id = "01", session = "01", group = "all", sampRate = sampRate, 
    filter = "raw", ccf = "", s1Name = s1Name, s2Name = s2Name, uid = "all_01_01", 
    class = c("MEA","list"))), class = "MEAlist", nId = 1L, n = 1L, groups = "all", sampRate = sampRate, 
    filter = "raw", s1Name = s1Name, s2Name = s2Name, ccf = "")
  return(mea)
}

# set the path to the data folders
if (Sys.getenv("LOGNAME") == "vilya") {
  dt.path  = "/Users/vilya/Documents/MSYNC/data"
} else {
  dt.path = "/media/emba/emba-2/MSYNC/data"
}

```

<style type="text/css">
  .main-container {
    max-width: 1100px;
    margin-left: auto;
    margin-right: auto;
  }
</style>

# Introduction  

This R Markdown script compares pseudosynchrony to synchrony values for the MSYNC project. The data was preprocessed before being read into this script. We use two approaches described in Moulder et al. (2018, Psychol Methods) to test the following hypotheses: "Synchrony does not exist between sections of size m in these two time series" (section sliding) and, if the first hypothesis is rejected, "There is no time dependency at all between these two time series" (data shuffling). We use the same settings as when computing synchrony to measure synchrony (windowed-lagged cross-correlation with the same timing settings). 

## Package versions

The following packages are used in this RMarkdown file: 
  
```{r lib_versions, echo=F}

print(R.Version()$version.string)

for (package in ls.packages) {
  print(sprintf("%s version %s", package, packageVersion(package)))
}

# set number of permutations
n = 100

```

# MEA data

```{r prep_mea}

if (!file.exists(file.path(dt.path, "preprocessedMEA", "df_psync.csv"))) {
  
  # create a dataframe
  df.psync = data.frame()
  
  # check if CT has been run before
  if (!file.exists(file.path(dt.path, "preprocessedMEA", "df_psync-CT.csv"))) {
    # start with the conversation task 
    attach(file.path(dt.path, "preprocessedMEA", "MEA_CT.Rdata"), name = 'CT')
    for (meth in c("seg", "data")) {
      df.mea = pseudosync(meth, mea.scaled, 
                              sampRate = 120, 
                              lagSec = 5,
                              winSec = 30, 
                              incSec = 15, 
                              n = n)
      df.mea = df.mea %>% 
        mutate(
          dyad = sprintf("MSYNC_%s", gsub("all_(.+)_0.*", "\\1", name)),
          task = "CT",
          method = meth
        ) %>%
        merge(., df.ccf.agg %>% ungroup() %>% 
                filter(position == "B" & measure == "mean") %>%
                select(dyad, phase, MEA.sync))
      df.psync = rbind(df.psync, df.mea)
      write_csv(df.psync, file.path(dt.path, "preprocessedMEA", "df_psync-CT.csv"))
    }
    # detach the CT data
    detach('CT')
  } else {
    df.psync = read_csv(file.path(dt.path, "preprocessedMEA", "df_psync-CT.csv"))
  }

  # check if CT has been run before
  if (!file.exists(file.path(dt.path, "preprocessedMEA", "df_psync-MG.csv"))) {
    # at the mirror game
    attach(file.path(dt.path, "preprocessedMEA", "MEA_MG.Rdata"), name = 'MG')
    for (meth in c("seg")) { # ,"data"
      df.mea = pseudosync(meth, mea.scaled,
                              sampRate = 120,
                              lagSec = 2,
                              winSec = 30,
                              incSec = 1,
                              n = n)
      df.mea = df.mea %>%
        mutate(
          dyad  = sprintf("MSYNC_%s", gsub("all_(.+)_0.*", "\\1", name)),
          task  = "MG",
          method = meth,
          phase = as.numeric(substr(name, nchar(name), nchar(name)))
        ) %>%
        merge(., df.ccf.agg %>% ungroup() %>%
                filter(position == "B" & measure == "mean") %>%
                select(dyad, phase, MEA.sync))
      df.psync = rbind(df.psync, df.mea)
      write_csv(df.psync, file.path(dt.path, "preprocessedMEA", "df_psync-MG.csv"))
    }
    # detach the MG data
    detach('MG')
  } else {
    df.mea = read_csv(file.path(dt.path, "preprocessedMEA", "df_psync-MG.csv"))
    df.psync = rbind(df.psync, df.mea)
  }
  
  # save the pseudosynchrony values
  write_csv(df.psync, file.path(dt.path, "preprocessedMEA", "df_psync.csv"))
  
} else {
  df.psync = read_csv(file.path(dt.path, "preprocessedMEA", "df_psync.csv"))
}


```

```{r comp_mea}

df.pagg = df.psync %>%
  group_by(dyad, task, method) %>%
  summarise(
    psync    = mean(as.numeric(psync)),
    MEA.sync = mean(MEA.sync)
  ) %>%
  pivot_longer(cols = c(psync, MEA.sync)) %>%
  mutate_if(is.character, as.factor)

aov.CT.seg = anovaBF( value ~ name, 
                  df.pagg %>% filter(task == "CT" & method == "seg"))

aov.CT.seg@bayesFactor
interpret_bf(aov.CT.seg@bayesFactor$bf, log = T)

aov.CT.data = anovaBF( value ~ name, 
                  df.pagg %>% filter(task == "CT" & method == "data"))

aov.CT.data@bayesFactor
interpret_bf(aov.CT.data@bayesFactor$bf, log = T)

p1a = df.pagg %>% 
  filter(task == "CT" & method == "seg") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Conversation task: segments", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

p1b = df.pagg %>% 
  filter(task == "CT" & method == "data") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Conversation task: data shuffling", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

aov.MG = anovaBF( value ~ name,
                  df.pagg %>% filter(task != "CT"))

aov.MG@bayesFactor
interpret_bf(sort(aov.MG@bayesFactor$bf, decreasing = T)[1], log = T)

p2 = df.pagg %>%
  filter(task != "CT") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Mirror game",
       x = "",
       y = "") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size = 12))

ggarrange(p1a, p1b, p2, 
          ncol = 2)

```

For the mirror game, synchrony credibly exceeds pseudosynchrony based on segments; thus, we do not compute pseudosynchrony based on data. For the conversation task, synchrony only exceeds pseudosynchrony based on data. Let's see whether we have at least some dyads that exceeded pseudosynchrony based on segments in the conversation task. 

```{r mea_sub}

# initialise a dataframe
df.sub = data.frame()

# loop through dyads
for (d in unique(df.psync$dyad)) {
  df.seg = df.psync %>% filter(method == "seg" & dyad == d & task == "CT")
  t = ttestBF(x = df.seg$psync, mu = mean(df.seg$MEA.sync))
  df.sub = rbind(df.sub, 
                 data.frame(
                   dyad   = d,
                   bf.log = t@bayesFactor$bf,
                   psync = mean(df.seg$psync),
                   MEA.sync = mean(df.seg$MEA.sync)
                 ))
}

df.sub = df.sub %>%
  mutate(
    direction = if_else(psync < MEA.sync,
                        "less", "greater"),
    relevant = if_else(direction == "less" & bf.log >= 3, "credible", "not credible"),
    interpretation = interpret_bf(t@bayesFactor$bf, log = T)
  ) %>%
  # merge with movement quantity
  merge(., read_csv(file.path(dt.path, "MSYNC_mea_CT.csv"), show_col_types = F) %>%
      select(dyad, total.mv) %>% distinct()) %>%
  mutate_if(is.character, as.factor) %>%
  write_csv(., file.path(dt.path, "preprocessedMEA", "df_psync_sub.csv"))

df.sub %>% group_by(relevant) %>% count()

# does it have anything to do with the overall movement quantity?
aov.CT.mv = anovaBF(total.mv ~ relevant, data = df.sub)

# nope, there is no difference between those
aov.CT.mv@bayesFactor

```

About half the dyads did not exceed pseudosynchrony when shuffling the segments. We might want to come back and investigate this later. 

# Speech data

## Individual level: turn-based pseudosynchronisation

For turn-based pseudosynchronisation, this script uses an approach described in Moulder et al. (2018, *Psychol Methods*) to test the following hypothesis: "Synchrony does not exist between sections of size *m* in these two time series" (section sliding). This segment shuffling, from Moulder et al., "requires researchers to cut a time series *X* into shorter sections of size *m* which are randomly appended to one another to create a new time series *Xs* until no section is in its original position". This new time series is then paired with an unchanged time series *Y*. Since the synchronisation is already based on sections  or speech turns in the conversation, no data shuffling will be performed. Since each dyad can have a unique amount of turns, no dyad shuffling will be performed. 

For each speaker in each task, the order of the previous turns are shuffled `r n` times while the order of the current turns remain unchanged. Note that no check for uniqueness is performed. In the end, an average for this specific speaker and task is calculated from the `r n` pseudosynchrony values. 

```{r indi_turn}

filename = "indi_st-shuffle.RData"

if (!file.exists(filename)) {
  
  speaker  = c()
  psyncint = c()
  psyncpit = c()
  psyncart = c()
  
  df = read_csv(file.path(dt.path, "preprocessedAudio", "OUT_turns.csv"), 
                show_col_types = F) %>% 
    mutate(speaker = paste(name, speaker, sep = "_")) %>%
    select(c(speaker, pit_turn, pit_prev_turn, 
             int_turn, int_prev_turn, 
             art_prev_turn, art_turn))

  for (s in unique(df$speaker)) {
    speaker = c(speaker, rep(s, times = n))
    df.sel = df %>% filter(speaker == s)
    for (i in 1:n) {
      # shuffling 
      df.sel$pit_prev  = sample(df.sel$pit_prev_turn)
      df.sel$int_prev  = sample(df.sel$int_prev_turn)
      df.sel$art_prev  = sample(df.sel$art_prev_turn)
      psyncint = c(psyncint, abs(cor(df.sel$int_turn,df.sel$int_prev, use = "na.or.complete")))
      psyncpit = c(psyncpit, abs(cor(df.sel$pit_turn,df.sel$pit_prev, use = "na.or.complete")))
      psyncart = c(psyncart, abs(cor(df.sel$art_turn,df.sel$art_prev, use = "na.or.complete")))
    }
  }
  df.s_shuffle = data.frame(speaker,psyncint, psyncpit, psyncart)
  save(df.s_shuffle,file = file.path(dt.path, "preprocessedAudio", filename))
} else {
  load(filename)
}

```

```{r indi_stats}

df.sync = read_csv(file.path(dt.path, "preprocessedAudio", "OUT_sync-indi.csv"), 
                show_col_types = F) %>% 
  mutate(
    speaker = paste(name, speaker, sep = "_")
  ) %>%
  select(c(speaker, pit_sync, int_sync, art_sync))

df.agg  = df.s_shuffle %>% group_by(speaker) %>%
  summarise(
    pit_psync  = mean(psyncpit),
    int_psync  = mean(psyncint),
    art_psync  = mean(psyncart)
  )

df.agg = merge(df.sync,df.agg)

res = ttestBF(x = df.agg[!is.na(df.agg$pit_sync),]$pit_sync,
        y = df.agg[!is.na(df.agg$pit_sync),]$pit_psync,
        paired = T) 
res
res@bayesFactor[["bf"]]
res = ttestBF(x = df.agg[!is.na(df.agg$int_sync),]$int_sync,
        y = df.agg[!is.na(df.agg$int_sync),]$int_psync,
        paired = T) 
res
res@bayesFactor[["bf"]]
res = ttestBF(x = df.agg[!is.na(df.agg$art_sync),]$art_sync,
        y = df.agg[!is.na(df.agg$art_sync),]$art_psync,
        paired = T)  
res
res@bayesFactor[["bf"]]


p1 = df.agg %>% 
  pivot_longer(cols = c(pit_sync, pit_psync)) %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Turn-based pitch sync", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

p2 = df.agg %>% 
  pivot_longer(cols = c(int_sync, int_psync)) %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Turn-based int sync", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

p3 = df.agg %>% 
  pivot_longer(cols = c(art_sync, art_psync)) %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Turn-based art sync", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

ggarrange(p1, p2, p3, ncol = 3)

```

The t-tests show that there is a significant difference between the pseudosynchronisation values obtained through segment shuffling and the real synchronisation values in the case of turn-based synchronisation of intensity and articulation rate, with the real synchronisation values being higher. However, for pitch this was not credibly the case. 

## Dyad level: timecourse pseudosynchrony based on CCF

We again use segment shuffling to compare pseudosynchrony and synchrony values on the dyad level. Pitch and intensity synchrony was calculated using the CCF function from rMEA. Therefore, we use the same function with the same window size but with shuffled windows for calculating pseudosynchrony.

For each speaker in each task, their time series is shuffled `r n/2` times and then paired with the unchanged time series of their partner in the dyad. Note that no check for uniqueness is performed. In the end, an average for this specific dyad and task is calculated from the `r n` pseudosynchrony values. 

```{r dyad-s}

filename = "dyad_s-shuffle.RData"

if (!file.exists(file.path(dt.path, "preprocessedAudio", filename))) {
  
  # create new data frame for pseudosync values
  cols = c("dyad", "task", "pit_psync_MEA", "int_psync_MEA")
  df.psync = data.frame(matrix(nrow = 0, ncol = length(cols)))
  colnames(df.psync) = cols
  
  # load actual sync values
  df.dyad = read_csv(file.path(dt.path, "preprocessedAudio", "OUT_dyad.csv"), 
                               show_col_types = F)
  
  sr = 100
  
  # go through all dyads
  for (i in 1:nrow(df.dyad)) {
    # load the respective data of continuous pitch and intensity 
    ptn = paste(df.dyad$dyad[i], df.dyad$task[i], ".*", "cont.csv", sep = "_")
    fls = list.files(pattern = ptn, path = file.path(dt.path, "preprocessedAudio"))
    df_L = read_csv(file.path(dt.path, "preprocessedAudio", fls[1]), 
                      show_col_types = F, col_types = cols(.default = "d")) 
    df_R = read_csv(file.path(dt.path, "preprocessedAudio", fls[2]), 
                      show_col_types = F, col_types = cols(.default = "d")) 
    # resample to 100Hz
    L_pit = df_L$pitch
    L_pit[is.na(L_pit)] = 0
    L_pit = signal::resample(L_pit,1,1000/sr) 
    L_int = df_L$int
    L_int[is.na(L_int)] = 0
    L_int = signal::resample(L_int,1,1000/sr) 
    R_pit = df_R$pitch
    R_pit[is.na(R_pit)] = 0
    R_pit = signal::resample(R_pit,1,1000/sr) 
    R_int = df_R$int
    R_int[is.na(R_int)] = 0
    R_int = signal::resample(R_int,1,1000/sr) 
    # create fakeMEA and divide into segments
    mea_int  = fakeMEA(L_int,R_int,sr,"int_L","int_R")
    mea_pit  = fakeMEA(L_pit,R_pit,sr,"pit_L","pit_R")
    mea_int_L = split(mea_int[["all_01_01"]][["MEA"]][["s1Name"]],
                      floor(seq_along(mea_int[["all_01_01"]][["MEA"]][["s1Name"]])/16))
    mea_int_R = split(mea_int[["all_01_01"]][["MEA"]][["s2Name"]],
                      floor(seq_along(mea_int[["all_01_01"]][["MEA"]][["s2Name"]])/16))
    mea_pit_L = split(mea_pit[["all_01_01"]][["MEA"]][["s2Name"]],
                      floor(seq_along(mea_pit[["all_01_01"]][["MEA"]][["s1Name"]])/16))
    mea_pit_R = split(mea_pit[["all_01_01"]][["MEA"]][["s2Name"]],
                      floor(seq_along(mea_pit[["all_01_01"]][["MEA"]][["s2Name"]])/16))
    # shuffle each side n/2 times
    for (j in 1:(n/2)) {
      
      # shuffling left
      mea_int[["all_01_01"]][["MEA"]][,2] = unlist(mea_int_R)
      mea_int[["all_01_01"]][["MEA"]][,1] = unlist(sample(mea_int_L))
      mea_int = MEAccf(mea_int,2,16,8)
      mea_pit[["all_01_01"]][["MEA"]][,2] = unlist(mea_pit_R)
      mea_pit[["all_01_01"]][["MEA"]][,1] = unlist(sample(mea_pit_L))
      mea_pit = MEAccf(mea_pit,2,16,8)
      # create new row with mean of peaks of windows
      new = c(df.dyad$dyad[i],
              df.dyad$task[i],
              mean(apply(mea_int$all_01_01$ccf,1,max)),
              mean(apply(mea_pit$all_01_01$ccf,1,max)))
      df.psync[nrow(df.psync) + 1,] = new      
      
      # shuffling right
      mea_int[["all_01_01"]][["MEA"]][,2] = unlist(sample(mea_int_R))
      mea_int[["all_01_01"]][["MEA"]][,1] = unlist(mea_int_L)
      mea_int = MEAccf(mea_int,2,16,8)
      mea_pit[["all_01_01"]][["MEA"]][,2] = unlist(sample(mea_pit_R))
      mea_pit[["all_01_01"]][["MEA"]][,1] = unlist(mea_pit_L)
      mea_pit = MEAccf(mea_pit,2,16,8)
      # create new row with mean of peaks of windows
      new = c(df.dyad$dyad[i],
              df.dyad$task[i],
              mean(apply(mea_int$all_01_01$ccf,1,max)),
              mean(apply(mea_pit$all_01_01$ccf,1,max)))
      df.psync[nrow(df.psync) + 1,] = new
    }
  }
  # save everything
  save(df.psync, file = file.path(dt.path, "preprocessedAudio", filename))
} else {
  load(file.path(dt.path, "preprocessedAudio", filename))
}

```

```{r dyad-s_stats, message=F}

df.sync = read_csv(file.path(dt.path, "preprocessedAudio", "OUT_dyad.csv"), 
                   show_col_types = F) %>% 
  select(c(dyad, task, pit_sync_MEA, int_sync_MEA))

df.agg  = df.psync %>% 
  mutate(
    pit_psync_MEA = as.numeric(pit_psync_MEA),
    int_psync_MEA = as.numeric(int_psync_MEA)
  ) %>%
  group_by(dyad, task) %>%
  summarise(
    pit_psync_MEA  = mean(pit_psync_MEA),
    int_psync_MEA  = mean(int_psync_MEA)
  )

df.agg = merge(df.sync,df.agg) 

res = ttestBF(x = df.agg[!is.na(df.agg$pit_sync_MEA),]$pit_sync_MEA,
        y = df.agg[!is.na(df.agg$pit_sync_MEA),]$pit_psync_MEA,
        paired = T) 
res
res@bayesFactor[["bf"]]
res = ttestBF(x = df.agg[!is.na(df.agg$int_sync_MEA),]$int_sync_MEA,
        y = df.agg[!is.na(df.agg$int_sync_MEA),]$int_psync_MEA,
        paired = T) 
res
res@bayesFactor[["bf"]] 


p1 = df.agg %>% 
  pivot_longer(cols = c(pit_sync_MEA, pit_psync_MEA)) %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Cont pitch sync", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

p2 = df.agg %>% 
  pivot_longer(cols = c(int_sync_MEA, int_psync_MEA)) %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Cont int sync", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

ggarrange(p1, p2, ncol = 3)



```

The t-tests show that there is a significant difference between the pseudosynchrony values obtained through segment shuffling and the real synchrony values in the case of MEA-based CCF synchrony of intensity and pitch, with the real synchrony values being higher.

# OpenFace data

```{r prep_of}

if (!file.exists(file.path(dt.path, "preprocessedOF", "df_psync.csv"))) {
  
  # create a dataframe
  df.psync = data.frame()
  
  # only do the conversation task 
  attach(file.path(dt.path, "preprocessedOF", "OpenFace_CT.Rdata"), name = 'CT')
  for (meth in c("seg")) {
    df.mea = pseudosync(meth, 
                        ls.fakeAU, 
                        sampRate = 120, 
                        lagSec = 2, winSec = 7, incSec = 4, 
                        n = n)
    df.mea = df.mea %>% 
      mutate(
        dyad = gsub("(.+)_CT.*", "\\1", name),
        phase = "CT", 
        method = meth,
        key  = gsub(".*_CT_(.+)", "\\1", name),
        psync = as.numeric(psync)
      ) %>%
      merge(., readRDS(file.path(dt.path, "MSYNC_AU_sync_CT.rds")) %>% 
              ungroup() %>% 
              filter(position == "B" & measure == "mean") %>%
              select(dyad, phase, key, OF.sync))
    df.psync = rbind(df.psync, df.mea)
  }
  df.psync = rbind(df.psync, df.mea)
  # detach the CT data
  detach('CT')
  
  # save the pseudosynchrony values
  write_csv(df.psync, file.path(dt.path, "preprocessedOF", "df_psync.csv"))
  
} else {
  df.psync = read_csv(file.path(dt.path, "preprocessedOF", "df_psync.csv"))
}


```

```{r comp_of}

df.pagg = df.psync %>%
  mutate(
    type = if_else(substr(key, 1, 2) == "AU", "AU", "pose")
  ) %>%
  group_by(dyad, type) %>%
  summarise(
    psync    = mean(psync),
    OF.sync  = mean(OF.sync)
  ) %>%
  pivot_longer(cols = c(psync, OF.sync)) %>%
  mutate_if(is.character, as.factor)

aov.CT.AU = anovaBF( value ~ name , 
                  df.pagg %>% filter(type == "AU"))

aov.CT.AU@bayesFactor
interpret_bf(aov.CT.AU@bayesFactor$bf, log = T)

aov.CT.PS = anovaBF( value ~ name , 
                  df.pagg %>% filter(type == "pose"))

aov.CT.PS@bayesFactor
interpret_bf(aov.CT.PS@bayesFactor$bf, log = T)

p1 = df.pagg %>% 
  filter(type == "AU") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Conversation task: AUs", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

p2 = df.pagg %>% 
  filter(type == "pose") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Conversation task: pose", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

ggarrange(p1, p2, ncol = 2)

```



# OpenPose data

```{r prep_op, eval=F}

if (!file.exists(file.path(dt.path, "preprocessedOP", "df_psync.csv"))) {
  
  # create a dataframe
  df.psync = data.frame()
  
  for (task in c("CT", "MG")) {
    # get the data
    attach(file.path(dt.path, "preprocessedOP", 
                     sprintf("OpenFace_%s.Rdata", task)), name = task)
    for (meth in c("seg", "data")) {
      df.mea = pseudosync(meth, ls.fakeAU, 
                            sampRate = 120, 
                            lagSec = 2, winSec = 7, incSec = 4, 
                            n = n)
      df.mea = df.mea %>% 
        mutate(
          dyad = gsub(sprintf("(.+)_%s.*", task), "\\1", name),
          phase = task,
          method = meth,
          key  = gsub(sprintf(".*_%s_(.+)", task), "\\1", name),
          psync = as.numeric(psync)
        ) %>%
        merge(., readRDS(file.path(dt.path, 
                                   sprintf("MSYNC_AU_sync_%s.rds"))) %>% 
                ungroup() %>% 
                filter(position == "B" & measure == "mean") %>%
                select(dyad, phase, key, OF.sync))
      df.psync = rbind(df.psync, df.mea)
    }
    # detach the data
    detach(task)
    
  }
  
  # save the pseudosynchrony values
  write_csv(df.psync, file.path(dt.path, "preprocessedOF", "df_psync.csv"))
  
} else {
  df.psync = read_csv(file.path(dt.path, "preprocessedOF", "df_psync.csv"))
}


```