---
title: "MSYNC: pseudosynchrony"
author: "I. S. Plank"
date: "`r Sys.Date()`"
output: pdf_document
geometry: margin=0.4in
---
  
```{r settings, include=FALSE}

knitr::opts_chunk$set(echo = T, warning = F, message = F, fig.align = 'center', fig.width = 8, fig.height = 3)
ls.packages = c("knitr",# kable
    "tidyverse",        # tibble stuff, ggplot
    "ggpubr",           # ggarrange
    "BayesFactor",      # anovaBF
    "effectsize",       # interpretBF
    "ggrain",           # geom_rain
    "rMEA"
)

lapply(ls.packages, library, character.only=TRUE)

# graph settings 
c_light = "#a9afb2"; c_light_highlight = "#8ea5b2"; c_mid = "#6b98b2" 
c_mid_highlight = "#3585b2"; c_dark = "#0072b2"; c_dark_highlight = "#0058b2" 
c_green = "#009E73"
sz = 1
a = 0.5

# custom colour palette
custom.col = c(c_dark_highlight, "#CC79A7", "#009E73", "#D55E00")

# scale function for vector
scale_this = function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

# load pseudosync_seg function
source("pseudosync_seg.R")

# set the path to the data folders
dt.path  = "/Users/vilya/Documents/MSYNC/data"

```

<style type="text/css">
  .main-container {
    max-width: 1100px;
    margin-left: auto;
    margin-right: auto;
  }
</style>
  
# S1 Introduction
  
This R Markdown script compares pseudosynchrony to synchrony values for the MSYNC project. The data was preprocessed before being read into this script. We use an approach described in Moulder et al. (2018, Psychol Methods) to test the following hypothesis: "Synchrony does not exist between sections of size m in these two time series" (section sliding). Then, we use the same settings as when computing synchrony to measure synchrony (windowed-lagged cross-correlation with the same timing settings). 

## Package versions

The following packages are used in this RMarkdown file: 
  
```{r lib_versions, echo=F}

print(R.Version()$version.string)

for (package in ls.packages) {
  print(sprintf("%s version %s", package, packageVersion(package)))
}

# set number of permutations
n = 50

```

## MEA data

```{r prep_mea}

if (!file.exists(file.path(dt.path, "preprocessedMEA", "df_psync.csv"))) {
  
  # create a dataframe
  df.psync = data.frame()
  
  # start with the conversation task 
  attach(file.path(dt.path, "preprocessedMEA", "MEA_CT.Rdata"), name = 'CT')
  df.mea = pseudosync_seg(mea.scaled, 
                          sampRate = 120, 
                          lagSec = 5,
                          winSec = 30, 
                          incSec = 15, 
                          n = n)
  df.mea = df.mea %>% 
    mutate(
      dyad = sprintf("MSYNC_%s", gsub("all_(.+)_0.*", "\\1", name)),
      task = "CT"
    ) %>%
    merge(., df.ccf.agg %>% ungroup() %>% 
            filter(position == "B" & measure == "mean") %>%
            select(dyad, phase, MEA.sync))
  df.psync = rbind(df.psync, df.mea)
  # detach the CT data
  detach('CT')
  
  # at the mirror game  
  attach(file.path(dt.path, "preprocessedMEA", "MEA_MG.Rdata"), name = 'MG')
  df.mea = pseudosync_seg(mea.scaled, 
                          sampRate = 120, 
                          lagSec = 2,
                          winSec = 30, 
                          incSec = 1, 
                          n = n)
  df.mea = df.mea %>% 
    mutate(
      dyad  = sprintf("MSYNC_%s", gsub("all_(.+)_0.*", "\\1", name)),
      task  = "MG",
      phase = as.numeric(substr(name, nchar(name), nchar(name)))
    ) %>%
    merge(., df.ccf.agg %>% ungroup() %>% 
            filter(position == "B" & measure == "mean") %>%
            select(dyad, phase, MEA.sync))
  df.psync = rbind(df.psync, df.mea)
  # detach the MG data
  detach('MG')
  
  # save the pseudosynchrony values
  write_csv(df.psync, file.path(dt.path, "preprocessedMEA", "df_psync.csv"))
  
} else {
  df.psync = read_csv(file.path(dt.path, "preprocessedMEA", "df_psync.csv"))
}


```

```{r comp_mea}

df.pagg = df.psync %>%
  group_by(dyad, task) %>%
  summarise(
    psync    = mean(psync),
    MEA.sync = mean(MEA.sync)
  ) %>%
  pivot_longer(cols = c(psync, MEA.sync)) %>%
  mutate_if(is.character, as.factor)

aov.CT = anovaBF( value ~ name, 
                  df.pagg %>% filter(task == "CT"))

aov.CT@bayesFactor
interpret_bf(aov.CT@bayesFactor$bf, log = T)

p1 = df.pagg %>% 
  filter(task == "CT") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Conversation task", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

aov.MG = anovaBF( value ~ name, 
                  df.pagg %>% filter(task != "CT"))

aov.MG@bayesFactor
interpret_bf(sort(aov.MG@bayesFactor$bf, decreasing = T)[1], log = T)

p2 = df.pagg %>% 
  filter(task != "CT") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Mirror game", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

ggarrange(p1, p2, ncol = 2)

```

Synchrony in CT was not higher than pseudosync. Therefore, we will not analyse this any further for now until we figure it out. However, synchrony was higher in the MG task, so we can use these values. 

## OpenPose data


## OpenFace data

```{r prep_of}

if (!file.exists(file.path(dt.path, "preprocessedOF", "df_psync.csv"))) {
  
  # create a dataframe
  df.psync = data.frame()
  
  # start with the conversation task 
  attach(file.path(dt.path, "preprocessedOF", "OpenFace_CT.Rdata"), name = 'CT')
  df.mea = pseudosync_seg(ls.fakeAU, 
                          sampRate = 120, 
                          lagSec = 2, winSec = 7, incSec = 4, 
                          n = n)
  df.mea = df.mea %>% 
    mutate(
      dyad = gsub("(.+)_CT.*", "\\1", name),
      phase = "CT", 
      key  = gsub(".*_CT_(.+)", "\\1", name),
      psync = as.numeric(psync)
    ) %>%
    merge(., readRDS(file.path(dt.path, "MSYNC_AU_sync_CT.rds")) %>% 
            ungroup() %>% 
            filter(position == "B" & measure == "mean") %>%
            select(dyad, phase, key, OF.sync))
  df.psync = rbind(df.psync, df.mea)
  # detach the CT data
  detach('CT')
  
  # save the pseudosynchrony values
  write_csv(df.psync, file.path(dt.path, "preprocessedOF", "df_psync.csv"))
  
} else {
  df.psync = read_csv(file.path(dt.path, "preprocessedOF", "df_psync.csv"))
}


```

```{r comp_of}

df.pagg = df.psync %>%
  mutate(
    type = if_else(substr(key, 1, 2) == "AU", "AU", "pose")
  ) %>%
  group_by(dyad, type) %>%
  summarise(
    psync    = mean(psync),
    OF.sync  = mean(OF.sync)
  ) %>%
  pivot_longer(cols = c(psync, OF.sync)) %>%
  mutate_if(is.character, as.factor)

aov.CT.AU = anovaBF( value ~ name , 
                  df.pagg %>% filter(type == "AU"))

aov.CT.AU@bayesFactor
interpret_bf(aov.CT.AU@bayesFactor$bf, log = T)

aov.CT.PS = anovaBF( value ~ name , 
                  df.pagg %>% filter(type == "pose"))

aov.CT.PS@bayesFactor
interpret_bf(aov.CT.PS@bayesFactor$bf, log = T)

p1 = df.pagg %>% 
  filter(task == "CT") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Conversation task", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

aov.MG = anovaBF( value ~ name, 
                  df.pagg %>% filter(task != "CT"))

aov.MG@bayesFactor
interpret_bf(sort(aov.MG@bayesFactor$bf, decreasing = T)[1], log = T)

p2 = df.pagg %>% 
  filter(task != "CT") %>%
  ggplot(., aes(x = name, y = value, fill = name, colour = name)) + #
  geom_rain(rain.side = 'f1x1',
            boxplot.args = list(color = "black", outlier.shape = NA, show_guide = FALSE, alpha = a),
            violin.args = list(color = "black", outlier.shape = NA, alpha = a),
            point.args = list(show_guide = FALSE, alpha = a)
            ) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), colour = "black") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2,
               aes(group = name)) +
  stat_summary(fun = mean, geom = "point", shape = 5, size = 2,
               aes(group = name), colour = "black") +
  scale_fill_manual(values = custom.col[c(1,3)]) +
  scale_colour_manual(values = custom.col[c(1,3)]) +
  labs(title = "Mirror game", 
       x = "", 
       y = "") +
  theme_bw() + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5), 
        text = element_text(size = 12))

ggarrange(p1, p2, ncol = 2)

```